Review questions list

### 2020-10-14 docs/revision/reply.tex
added all quotes: reviewer 2and3

>>>>

	{\bfseries\large Reviewer 2}

	\begin{quote}
	 Please, reread the paper to correct some misspelling words. For example, Abstract (line 3): should it be "researchers"? Another example in "Introduction", page 1, column 2, line 35: "Snell's Total" instead of "Snell?s Total".
	\end{quote}

	\begin{quote}
	The authors wrote, "The most important contribution of this research is the use of
the GAN phase, where the available data is expanded to be
used in the training phase". Why use a Generative adversarial network? What would be the advantages and disadvantages of a GAN approach over other possible data generators, such as evolutionary mutation functions? The authors should provide a comparison methodology and discuss differences between GAN and other data generators.
	\end{quote}

	\begin{quote}
	How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed?
	\end{quote}

	\begin{quote}
	Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.
	\end{quote}

	\begin{quote}
	Please, define which is RI (page 4, column 1, line 38).
	\end{quote}

	\begin{quote}
	How do the authors know the ANN is not overfitting in Fig. 3? Have the authors employed any validation during training? Please, provide the ANN models' performance on the validation by showing the validation MSE during training.
	\end{quote}

	\begin{quote}
	Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).
	\end{quote}

	{\bfseries\large Reviewer 3}

	\begin{quote}
	I suggest that the authors give more information about the stopping criteria of the GAN. As the author pointed out, human judgment has an important role in the generation of images and audio. So, could the known physical laws about PCF and SPR be used to replace the human role in the GAN system to improve the performance? How does the author verify the validity of the augmented samples?
	\end{quote}

	\begin{quote}
	 In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected?
	\end{quote}

	\begin{quote}
	In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation?
	\end{quote}

	\begin{quote}
	In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters. Could the authors discuss the reasons for the deviation and how to judge the validity of the calculation result?
	\end{quote}
